Twisted 11-dimensional supergravity, I

### 2021-08-05 draft.tex
typos
all chopped up

@@

\subsubsection{}
\label{sec:Linfty}

\subsection{The 11-dimensional theory}

We apply this construction to the case of the $L_\infty$ algebra $\cL_0 = \cL_0 (X)$ of \S \ref{sec:Linfty} resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$ and the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold. 
We thus obtain the structure of an $L_\infty$ algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$. 
One can immediately check that this defines a local $L_\infty$ algebra on the product manifold $X \times L$.

>>>>

\parsec 
\ingmar{a section defining polyvector fields; not sure where this belongs}
Equipped with this structure, the complex we have written maps in an obvious way into the complex of polyvector fields on~$X$. Recall that one defines
\deq{
  \PV^{i,j}(X) = \Omega^{0,j}(X, \wedge^i \T_X).
}
\ingmar{Wedges look super fucked up}
The complex $\PV^{\bu,\bu}$ is equipped with two natural differentials: the Dolbeault operator $\dbar$, of $(i,j)$-degree $(0,1)$, and the holomorphic divergence operator $\div$, which carries $(i,j)$-degree $(-1,0)$. Assigning total degree $- i + j$ to $\PV^{i,j}$ thus gives the total polyvector fields the structure of a bicomplex. We will use the shorthand notation $\PV^i = (\PV^{i,\bu}, \dbar )$ for the Dolbeault resolution of holomorphic $i$-polyvector fields.

\parsec[sec:Linfty]

Recall that an $L_\infty$ morphism $\Phi: \cL \rightsquigarrow \cL'$ is the same datum as a map of commutative dg algebras 
\deq{
  \Phi^*: C^\bu(\cL') \to C^\bu(\cL)
}
between their respective Lie algebra cochains. It follows from this that \emph{any} automorphism $\Phi$ of the free commutative algebra $C^\bu(\cL)$ defines a new model of the $L_\infty$ algebra $\cL$, for which the Chevalley--Eilenberg differential is obtained by conjugating $\d_\cL$ by~$\Phi$, and where $\Phi$ itself defines the $L_\infty$ isomorphism.

Let $\cL$ be the 
We consider the following two automorphisms

\subsection{Theories of BF type}

We apply this construction, taking $\lie{g}$ to be the sheaf of dg Lie algebras resolving divergence-free holomorphic vector fields on a Calabi--Yau manifold $X$, as discussed above, and $A$ to be the smooth de Rham complex $(\Omega^\bu(L) , \d_L)$ where $L$ is any smooth manifold. 
We thus obtain the structure of an $L_\infty$ algebra on $\cL_0(X) \otimes \Omega^{\bu}(L)$. 
One can immediately check that this defines a local $L_\infty$ algebra on the product manifold $X \times L$.

\parsec
For concreteness, we recall that the fields of the theory we have constructed on $\C^{2k+1}\times\R$ are given by the sheaf $\cE$ presented in the following diagram:
\begin{equation}
  \label{eq:sympfields} 
  \begin{tikzcd}[row sep = 1 ex]
    -n & -n + 1 & -1 & 0 \\ \hline
    \Omega^{0}(X;L) \ar[r] & \Omega^{1}(X;L) & 
     \PV^{1}(X; L) \ar[r] & \PV^{0}(X; L).
\end{tikzcd}
\end{equation}
We are using the shorthand notation $\PV^{i}(X;L) = (\PV^{i,\bu}(X)\otimes \Omega^*(L), \dbar + \d_{dR}))$, so that the pairing beween $\PV^i(X;L)$ and~$\Omega^i(X;L)$ is of degree $-\dim_\C(X) -\dim_\R(L)$. As such, the $\Z$-grading indicated in~\eqref{eq:sympfields} equips the sheaf of fields with a $(-1)$-shifted symplectic structure, provided that we choose the shift to be given by
\deq{
  n = \dim_\C(X) + \dim_\R(L) - 1.
}
Note, though, that the interactions we consider do not preserve this grading, and as such only define $\Z/2\Z$-graded theories. We denote the fields $(\beta,\gamma,\mu,\nu)$ respectively.

Recall further that we constructed two equivalent descriptions of the BF theory based on divergence-free holomorphic vector fields above. Since we are now in the context of a nondegenerate BV theory, the differential is Hamiltonian, and can be incorporated into the action functional by including a quadratic term; we do this from now on. The first action functional is obtained by considering the BF theory associated to the natural dg Lie structure on the complex modeling divergence-free vector fields (inherited from the Schouten bracket). This takes the form
\deq{
  I_\strict = \beta\partial_\Omega \mu + \frac{1}{2} \gamma [\mu,\mu] + \beta[\mu,\nu].
}
The other action is of infinite order, and is related to the BCOV action functional via the procedure outlined above \ingmar{or somewhere}. Explicitly, this action functional is given by 
\deq{
  I_\infty = \beta \partial_\Omega \mu + \frac{1}{1-\nu} (\partial \gamma) \mu^2,
}

\subsection{Relation to BCOV theory}

@@
